Papers

### 2024-07-24 quarto/index.qmd
update

* <a href="https://ai.meta.com/blog/meta-llama-3-1/" target="_blank">Llama 3.1 405B</a> is now openly available. <a href="https://x.com/astonzhangAZ/status/1815763885380747422" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
* Meet <a href="https://ai.meta.com/blog/meta-llama-3/" target="_blank">Llama 3</a>, our state-of-the-art open source large language model. <a href="https://x.com/astonzhangAZ/status/1780990210576441844" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a> (my *Llama for Developers* <a href="https://x.com/AIatMeta/status/1806757387677897206" target="_blank">podcast</a>)
* Join us for a 2024 research internship (filled, see you next time). <a href="https://twitter.com/astonzhangAZ/status/1731698624902402281" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>

>>>>

* <a href="https://ai.meta.com/blog/meta-llama-3-1/" target="_blank">Llama 3.1 405B</a> is now openly available. See Mark's thoughts on <a href="https://x.com/rowancheung/status/1815763595197616155" target="_blank">Llama 3 and beyond</a>. <a href="https://x.com/astonzhangAZ/status/1815763885380747422" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
* Meet <a href="https://ai.meta.com/blog/meta-llama-3/" target="_blank">Llama 3</a>, our state-of-the-art open source large language model. See my <a href="https://x.com/AIatMeta/status/1806757387677897206" target="_blank">podcast</a> for developers. <a href="https://x.com/astonzhangAZ/status/1780990210576441844" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
* Join us for a 2024 research internship (filled, see you next time). <a href="https://twitter.com/astonzhangAZ/status/1731698624902402281" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
